Persistence of seed mixture species: <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-14 R/model_persistence_markdown.Rmd
Update persistence

```{r}
load(file = here("data", "processed", "model_fcs_1.Rdata"))
load(file = here("data", "processed", "model_fcs_2.Rdata"))
load(file = here("data", "processed", "model_fcs_3.Rdata"))
```

>>>>

```{r}
load(file = here("data", "processed", "model_persistence_1.Rdata"))
load(file = here("data", "processed", "model_persistence_2.Rdata"))
load(file = here("data", "processed", "model_persistence_3.Rdata"))
```
